Effect of multiple reflection of the sky signal off the HERA element on the measurements of 21cm power spectrum

### 2015-11-06 DishReflectometry/Paper1_v0.tex
Edited last paragraph before section 3.2.

 The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz . In this paper, we investigate the performance of the individual HERA elements and resulting contribution of the instrument response to the delay spectrum. Reflectometry measurements  are carried out across wide bandwidth on a prototype HERA element in Green
Bank, WV (Figure \ref{fig:heradish}) and the results are interpreted in the light of delay spectrum technique. Section 2 describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer. Reflectometry measurements are described in section 3. Section 4 qualifies the performance of the HERA element as an interferometer for detection of the 21~cm power spectrum.

@@

Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
 Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the same delay $\tau $ in the Fourier domain whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\Delta \tau$. This additional delay extends the upper limit on the maximum geometric delay $\tau_{g}$ to $(\tau_{g}+\Delta \tau)$.
 Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected. If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish. Also, if we assume a $\Gamma_{a} =-10dB$ and $\Gamma_{d}= -20dB$, the second term in the expression of $\Sigma(\vec b, \nu)$ becomes negligible compared to the first and the third term of the expression and, therefore, can be neglected. \\

>>>>

The Hydrogen Epoch of Reionization Array (HERA) is a proposed array consisting of 568 14-m dishes in South Africa which will measure the 21~cm power spectrum between 100 to 200~MHz.
In this paper, we investigate the performance of the individual HERA elements and resulting contribution of the instrument response to the delay spectrum.
 Reflectometry measurements  are carried out across wide bandwidth on a prototype HERA element in Green
Bank, WV (Figure \ref{fig:heradish}) and the results are interpreted in the light of delay spectrum technique. Section 2 describes the delay spectrum for the ideal and non-ideal performance of a two element interferometer. Reflectometry measurements are described in section 3. Section 4 qualifies the performance of the HERA element as an interferometer for detection of the 21~cm power spectrum.

@@

Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. 
 Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay will be located at the same delay $\tau $ in the Fourier domain whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\Delta \tau$. This additional delay extends the upper limit on the maximum geometric delay $\tau_{g}$ to $(\tau_{g}+\Delta \tau)$.
 Thus, the correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected. 
 If the dish vertex is so constructed such that the reflection from the dish vertex is negligible i.e, $\Gamma_{d}<<1\ or = 0$ then the second and the third term of the $\Sigma$ vanish. Also, the second term in the expression of $\Sigma(\vec b, \nu)$ is negligible compared to the first and the third term of the expression and, therefore, can be neglected. \\
